### 2019-03-12 papers/journal/encoding.tex
removed duplicate text from 6.4 intro
updated univ encoding ref

\subsection{Universal condition}
\label{enc:univ-cond}
%
Recall that the specification for universal condition~\ref{eq:univcond} requires quantifier alternation. 
%
Most SAT solvers can not efficiently handle the quantifier in the formulas. 
% 
Although, it is possible to encode the universal condition~\ref{eq:univcond} as a SAT or SMT problem.
%
There is always a danger of a blow-up in the formula size, making it harder for the SAT solver to handle. 
%Which may blow up the formula size for the solver to solve.
% 
As an experiment, we have implemented a direct SMT version of the universal problem extending the current SMT encodings.
%
The basic idea is to conjunct the formula for each combination value of the quantified variable. 
%

@@

\subsection{Synthesis of VTS}
%In this section, we will present our synthesis method for
%the synthesis problems.

>>>>

\subsection{Universal condition}
\label{enc:univ-cond}
%
Recall that the specification for universal condition~\ref{sec:property} requires quantifier alternation. 
%
Most SAT solvers can not efficiently handle the quantifier in the formulas. 
% 
Although, it is possible to encode the universal condition as a SAT or SMT problem.
%
There is always a danger of a blow-up in the formula size, making it harder for the SAT solver to handle. 
%Which may blow up the formula size for the solver to solve.
% 
As an experiment, we have implemented a direct SMT version of the universal problem extending the current SMT encodings.
%
The basic idea is to conjunct the formula for each combination value of the quantified variable. 
%

@@

\subsection{Synthesis of VTS}
In this section, we will present our synthesis method for
the synthesis problems.
%
%We assume that certain properties of the partial input VTS always hold, for example, the activity of the molecules and well-fused constraints. 
%
%Whereas properties like stability and connectivity discussed in the previous sections may not.
%
Here, we use these two properties stability and connectivity against which we perform our synthesis. 
%
The encoding can be easily extended to accommodate other interesting properties.
